\thetitle

### 2018-01-12 TeX/manuscript.tex
more additions to 2.7

In the above network, the output neuron's value is calculated as a weighted sum of the inputs. While this algorithm is widely used in feed-forward neural networks, it assumes that the desired output value's relationship to it's inputs can be modelled by a weighted sum of the inputs.

@@

	\node[input] (i1) at (0,0) {Age 1};
	\node[input] (i2) at (4,0) {Age 2};

	\node[router] (r) at (2,2) {Router};

@@

	\node[output] (o1) at (2,6) {14};

@@

@@

>>>>

In the above network, the output neuron's value is calculated as a weighted sum of the inputs. While this algorithm is widely used in feed-forward neural networks, it assumes that the desired output value's relationship to it's inputs can be modelled by a weighted sum of the inputs.  \\

@@

	\node[input] (i1) at (0,0) {24 Years};
	\node[input] (i2) at (4,0) {8 Years};

	\node[font=\bf] (dum) at (6,2) {USE DIVISION};
	\node[router] (r) at (2,2) {Router};

@@

	\node[output] (o1) at (2,6) {3 Times as old};

@@

	\draw[->,line width=0.5mm](dum) -> (r) {};

@@

\caption{A network which yields the number of times a person is older than another.}

The 'Router' represents some function which decides which computational class should be used to compute the output. In the above network, we instructed the router to operate on input values using division, since that was how we detirmined that the task could be solved. \\

Of course, instructing the router as to which computation it should use in each input case defeats it's purpose. Instead, we may use conditional statements to determine which computation will be used. This allows us to construct networks which perform different classes of computation depending on the situation. One such network is shown below.

\caption{}
